%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \text{#3} & #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jackson Newman} \\ \vspace{1pt}
    \small Redwood City, CA, 94065 $|$ 650-649-8204 $|$ \href{mailto:jpnewman167@gmail.com}{\underline{jpnewman167@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/jacknewman/}{\underline{linkedin.com/in/jacknewman}} $|$
    \href{https://github.com/JNewman-cell/}{\underline{https://github.com/JNewman-cell/}} $|$
    \href{https://jacksonnewman.netlify.app/}{\underline{jacksonnewman.netlify.app/}}
\end{center}


%-----------EXPERIENCE-----------
\section{\textbf{Work Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
    {AMD}{\textbf{San Jose, CA}}
    {Software Engineer Intern, Internal Development Tooling}{June 2023 - September 2023}
    \resumeItemListStart
        \resumeItem{Accelerated Vivado constraint processing by 50\% with a new C++ pattern matching function.}
        \resumeItem{Developed unit tests achieving 100\% coverage to ensure performance and accuracy for Wildcard Matching.}
        \resumeItem{Reduced Vivado memory usage by 2\% by refactoring code to utilize Tessil C++ Hash map package.}
        \resumeItem{Automated memory, encryption tests, and key upgrades using Python, cutting testing time by 50\%.}
    \resumeItemListEnd

    \resumeSubheading
    {Shellie.us}{\textbf{San Francisco, CA}}
    {Full Stack Software Engineer Intern, MERN Stack}{June 2022 - September 2022}
    \resumeItemListStart
        \resumeItem{Developed a React-based hierarchical UI with dynamic modals and edit functionality for exhibits.}
        \resumeItem{Created REST API integrations for editing and saving exhibit data in the NoSQL backend database.}
        \resumeItem{Created reusable React components, improving maintainability and reducing development time by 30\%.}
        \resumeItem{Used React and Redux for state management, enhancing data consistency and reducing errors by 20\%.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{\textbf{Projects}}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\href{https://github.com/JNewman-cell/StockProjects}{\underline{\textbf{Historical Stock Information Visualization Website}}} 
            $|$ \emph{Flask, Python, Javascript, SQL, CI/CD, GitHub Actions, REST API}}{}
            \resumeItemListStart
            \resumeItem{Developed a Flask-based REST API with 6+ endpoints for database retrieval, enabling real-time data.}
            \resumeItem{Created a custom Trie data structure with 6000+ ticker prefix matching and market cap-based ranking.}
            \resumeItem{Implemented GitHub Actions testing pipeline for ticker search, validating 100\% of autocomplete accuracy.}
            \resumeItem{Improved stock info retrieval time by 80\% through optimized API design and local database storage.}
            \resumeItem{Developed a custom caching system that cut GitHub Actions workflow time by up to 60\%.}
        \resumeItemListEnd
        \resumeProjectHeading
            {\href{https://github.com/ucsb-cs156-s23/proj-courses-s23-7pm-2}{\underline{\textbf{REST API implementation and Database Management}}}
            $|$ \emph{Java, Javascript, React, PostgreSQL, Spring Boot, Maven, Swagger, Storybook}}
            {}
            \resumeItemListStart
            \resumeItem{Developed CRUD operations in a Java backend for PostgreSQL database, deploying 6 key functions.}
            \resumeItem{Reduced course search query volume by 60\% by implementing search by instructor SQL filters.}
            \resumeItem{Created a comprehensive testing suite to cover 100\% of query functionality, including error handling.}
            \resumeItem{Integrated frontend and backend testing into the CI/CD workflow, ensuring 100\% up time in production.}
        \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{AI Model Demonstration Wesbite}
            $|$ \emph{Flask, AWS, REST API, HTTP, JSON}}{}
            \resumeItemListStart
            \resumeItem{Configured and deployed 3 AWS EC2 Linux VMs for AI model performance testing and benchmarking.}
            \resumeItem{Deployed an end-to-end Flask web app with Nginx to showcase OpenAI-like LLM inference via HTTP.}
            \resumeItem{Benchmarked Llama.cpp and vLLM server with LLMPerf to determine the fastest LLM inference on CPU.}
            \resumeItem{Developed a Flask API server capable of handling hundreds of image generation requests per second.}
        \resumeItemListEnd
        \resumeProjectHeading
            {\href{https://github.com/JNewman-cell/CommuterHelper}{\underline{\textbf{Website for Daily Commute Information}}}
            $|$ \emph{React, Javascript, CSS, Bootstrap, OAuth, GCP, Firebase, Git}}{}
            \resumeItemListStart
            \resumeItem{Created 3 CRUD APIs for user commute information, including time, address, and destination.}
            \resumeItem{Configured Firebase for 1000+ users for secure user authentication and database storage.}
            \resumeItem{Utilized GCP Functions and Google Maps API for scheduled email sending and fastest route info.}
            \resumeItem{Designed and styled interactive interfaces using CSS, increasing usability and readability by 20\%.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California Santa Barbara}{\textbf{Santa Barbara, CA}}
      {Bachelor of Science in Computer Engineering}{September 2020 - June 2024}
    \resumeSubheading
      {3.7 GPA, Dean's Honors, Relevant Coursework:}{}
      {\small{Data Structures, Algorithms, Operating Systems, Machine Learning, AI, Embedded Systems, Web Development}}{}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C/C++, Java, Python, PostgreSQL, SQL, SQLite, JavaScript, HTML, CSS, JSON, YAML} \\
     \textbf{Frameworks}{: React, Node.js, Flask, Bootstrap, Material-UI, Storybook, Spring Boot} \\
     \textbf{Developer Tools}{: Git, Docker, Jira, Google Cloud Platform AWS, GitHub, Confluence, Perforce, NPM, Firebase, GitHub Actions, MongoDB, Jenkins} \\
     \textbf{Libraries}{: pandas, NumPy, TensorFlow, PyTorch, Keras, Seaborn, matplotlib } \\
    %  \resumeItemListStart
    %         \resumeItem{Demonstrated adeptness in Linux development at AMD through bash scripting and utilization of development tools, showcasing a strong grasp of environments and workflows.}
    %         \resumeItem{Experience in Agile/SCRUM development with Kanban, stand-ups, and Retrospectives.}
    %         \resumeItem{Skilled in refactoring legacy codebases to enhance efficiency and optimize performance.}
    %         \resumeItem{Experience automating and scripting testing and workflows using CI/CD tools.}
    % \resumeItemListEnd
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
